Binary Latent Representations for Efficient Ranking

### 2017-06-17 paper/paper.tex
Add some future work.

>>>>

There are a number of ways in which our work could be extended. An increasing number of recommender applications employ more sophisticated models using recurrent units for sequence representations or convolutional units for incorporating image data. Our approach can easily be applied in such models by simply replacing the topmost dot product or softmax layers with their binary equivalents.
